Lake Photic Zone Temperature across the Conterminous United States

### 2019-10-28 manuscript/manuscript.Rmd

>>>>

Using only easily obtainable metrics to estimate lake temperature was a primary focus in the creation of this model.  Several studies (e.g. [@piccolroaz2018predictability]) have used similar metrics with good results (RMSE=0.5 °C) to estimate lake temperature but were applied to a single, or a small number of lakes.  Other studies have used more complex models (e.g. GLM) to yield good results (RMSE = 1.62 °C for the epilimnion) at varying scales [@bruce2018multi; @hipsey2019general].  However, these models require more complex input variables which are not available for all lakes and may be biased towards large lakes.  Using the NLA data and simple metrics allowed this model to be applicable to any lake within the conterminous United States using minimal input data with a small increase in RMSE.  Additionally, this model is predictive and the model and data will be made publicly available.
